systemfit: A Package to Estimate\\ Simultaneous Equation Systems in \proglang{R}

### 2006-02-25 paper/trunk/systemfit_statistics.tex
the capitalization of all (sub)(sub)section headers is now in sentence-style (according to the guidelines of the JSS)
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@618 591db2bd-e0a0-4d22-8c19-2192dbb7da31
added footer for nested docs
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@633 591db2bd-e0a0-4d22-8c19-2192dbb7da31

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Statistical Background}\label{sec:statistics}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

In this section we provide the statistical background
of the functionality provided in the \pkg{systemfit} package.
After introducing notations and assumptions,
we provide the formulas to estimate linear equation systems.
Then, we shows how linear restrictions can be imposed.
Finally, some other relevant issues about estimation of equation systems
are discussed.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Statistical background}\label{sec:statistics}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

In this section we provide the statistical background
of the functionality provided by the \pkg{systemfit} package.
After introducing notations and assumptions,
we provide the formulas to estimate systems of linear equations.
We then demonstrate how to impose linear restrictions on parameters.
Finally, we present additional relevant issues about estimation of
equation systems.
